A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-10-02 paper/paper.tex
notes on a train II

At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.

The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans

>>>>

At the least, we propose an alternative vocabulary to
describe and discuss neuroscientific studies on the DMN.
%
In principle,
neuroscientific experiments can be designed that operationalize
the set of action, value, and state variables that determine
the behavior of RL systems. This makes proposed machine-learning
approach to DMN function not only practically computable but
also neuroscientifically falsifiable.
%
The DMN can be viewed as a smoothing kernel extending
from the relatively recent past to the relatively close future
that constantly estimates complex non-linear gain functions.
-> This is why neuroimaging research revealed activity increases in the DMN
when 
-> This may be why perfect memory has been evolutionarily de-selected,
although it is provably feasible by the neurobiological hardware in humans
